Matching Bullets

### 2015-11-28 imaging-paper.Rnw
trying for a complete analysis of the Hamby study
Start refactoring that second circle figure into loess

\begin{figure}[hbtp]
  \centering
\begin{subfigure}[b]{\linewidth}
\caption{Circle fit for each cross section of bullet 2, with part 1 of bullet 1 overlayed.\label{fig:circlefits}}{%
<<circlefits, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey30")) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), colour="black", size=1, alpha=0.2, 
             data = filter(db1, part==1, x == 100)[,c("y", "resid", "x")]) + ggtitle("Part 1 of Bullet 1 in black")
@
}
\end{subfigure}    
\begin{subfigure}[b]{\linewidth}
    \caption{Circle fit for each cross section of bullet 2, with part 2 of bullet 1 overlayed.\label{fig:circlefits2}}{%
<<circlefits2, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE,  cache=TRUE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey30")) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group =x), colour="black", size=1, alpha=0.2, 
             data = filter(db1, part==2, x == 100)[,c("y", "resid", "x")]) + ggtitle("Part 2 of Bullet 1 in black")
@    
}
\end{subfigure}
\caption{An example of a scan of a bullet land from one groove to the next. }
\end{figure}

If we perform a similar routine for part 2 of bullet 1, we obtain the figure given in Figure \ref{fig:circlefits2}.

@@

<<loess_step12, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Steps 1 and 2 of the Loess fit algorithm. The top panel is a plot of height values for part 1 of bullet 1 across different values of y, with x held constant at 243.75. The bottom panel is the same plot, but with the first and last 100 y values trimmed.', fig.pos='H', message=FALSE>>=
br111_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-1.x3p", sep = "/"))

@@

@@

In order to address the subjectivity involved in choosing a threshold level, we investigate this parameter more closely. Figure~\ref{fig:thresholds} shows the relationship between threshold and the maximal number of consecutive matching striae. For thresholds between 0.75 and 0.85 the number of CMS peaks at fifteen. On average, there are 6.6 CMS across the range of thresholds.
\begin{figure}
<<thresholds, echo=FALSE, fig.width = 7, fig.height = 3, out.width = '0.49\\textwidth'>>=
thresholds <- seq(0.3, 1.5, by = 0.025)
CMS <- thresholds %>% lapply(function(threshold) {
 lines <- striation_identify(lofX, threshold = threshold)
 cms <- CMS(lines$match)
 data.frame(threshold=threshold, maxCMS = as.numeric(rev(names(cms)))[1])
}) %>% bind_rows()

>>>>

\begin{figure}[hbtp]
  \centering
\caption{Circle fit for each cross section of bullet 2, with part 1 of bullet 1 overlayed.\label{fig:circlefits}}{%
<<circlefits, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey30")) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group = x), colour="black", size=1, alpha=0.2, 
             data = filter(db1, part==1, x == 100)[,c("y", "resid", "x")]) + ggtitle("Part 1 of Bullet 1 in black")
@

\end{figure}

@@

<<loess_step12, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE, fig.cap='Steps 1 and 2 of the Loess fit algorithm. The top panel is a plot of height values for part 1 of bullet 1 across different values of y, with x held constant at 243.75. The bottom panel is the same plot, but with the first and last 100 y values trimmed.', fig.pos='H', message=FALSE>>=
br111_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-1.x3p", sep = "/"))
br112_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-2.x3p", sep = "/"))
br113_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-3.x3p", sep = "/"))
br114_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-4.x3p", sep = "/"))
br115_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-5.x3p", sep = "/"))
br116_bullet <- get_bullet(paste(datadir,"Br1 Bullet 1-6.x3p", sep = "/"))

@@

<<loessfits, echo=FALSE, fig.width=10, fig.height=7, out.width='\\linewidth', warning=FALSE>>=
br111.groove <- get_grooves(br111_bullet)
br112.groove <- get_grooves(br112_bullet)
br113.groove <- get_grooves(br113_bullet)
br114.groove <- get_grooves(br114_bullet)
br115.groove <- get_grooves(br115_bullet)
br116.groove <- get_grooves(br116_bullet)

my.loess1 <- fit_loess(br111_bullet, br111.groove)
my.loess2 <- fit_loess(br112_bullet, br112.groove)
my.loess3 <- fit_loess(br113_bullet, br113.groove)
my.loess4 <- fit_loess(br114_bullet, br114.groove)
my.loess5 <- fit_loess(br115_bullet, br115.groove)
my.loess6 <- fit_loess(br116_bullet, br116.groove)

qplot(y, resid, data=subset(db2, x == 100), #colour=factor(x), 
      geom="line", size=I(1), colour=I("grey30")) + 
  facet_wrap(~part) + scale_colour_brewer(palette="Paired") +
  theme_bw() + theme(legend.position="bottom") + 
  geom_line(aes(y, resid, group =x), colour="black", size=1, alpha=0.2, 
             data = filter(db1, part==2, x == 100)[,c("y", "resid", "x")]) + ggtitle("Part 2 of Bullet 1 in black")
@

@@

In order to address the subjectivity involved in choosing a threshold level, we investigate this parameter more closely. Figure~\ref{fig:thresholds} shows the relationship between threshold and the maximal number of consecutive matching striae. For thresholds between 0.7 and 0.9 the number of CMS peaks at fifteen. On average, there are 6.6 CMS across the range of thresholds.
\begin{figure}
<<thresholds, echo=FALSE, fig.width = 7, fig.height = 3, out.width = '0.49\\textwidth'>>=
thresholds <- seq(0.3, 1.5, by = 0.025)
CMS <- thresholds %>% lapply(function(threshold) {
 lines <- striation_identify(lofX, threshold = threshold)
 cms <- CMS(lines$match)
 data.frame(threshold=threshold, maxCMS = as.numeric(rev(names(cms)))[1])
}) %>% bind_rows()
